<!--
% \VignetteIndexEntry{Using miniCRAN to identify package dependencies}
% \VignetteEngine{knitr::knitr}
% \VignettePackage{miniCRAN}
% \VignetteKeyword{miniCRAN}
--> 

# Using miniCRAN to identify package dependencies

## Introduction

In miniCRAN I expose two functions that provides information about dependencies:

* The function `pkgDep()` returns a character vector with the names of dependencies. Internally, ``pkgDep()`` is a wrapper around `tools::package_dependencies()`, a base R function that, well, tells you about package dependencies. My new function is in one way a convenience, but more importantly it sets different defaults (more about this later).

* The function `makeDepGraph()` creates an igraph representation of the dependencies.

Take a look at some examples.  I illustrate with the the package `chron`, because `chron` neatly illustrates the different roles of Imports, Suggests and Enhances:

* `chron` Imports the base packages graphics and stats. This means that `chron` internally makes use of graphics and stats and will always load these packages.

* `chron` Suggests the packages scales and ggplot2. This means that `chron` uses some functions from these packages in examples or in its vignettes.  However, these functions are not necessary to use `chron`

* `chron` Enhances the package `zoo`, meaning that it adds something to `zoo` packages. These enhancements are made available to you if you have `zoo` installed.


## A worked example using the package chron

The function `pkgDep()` exposes not only these dependencies, but also also all recursive dependencies. In other words, it answers the question which packages need to be installed to satsify all dependencies of dependencies.

This means that the algorithm is as follows:

* First retrieve a list of Suggests and Enhances, using a non-recursive dependency search
* Next, perform a recursive search for all Imports, Depends and LinkingTo

The resulting list of packages should then contain the complete list necessary to satisfy all dependencies. In code:

```{r init}
library(miniCRAN)
```


```{r pkgdep}
tags <- "chron"
pkgDep(tags, suggests=FALSE, enhances=FALSE, includeBasePkgs = TRUE)

pkgDep(tags, suggests = TRUE, enhances=FALSE)

pkgDep(tags, suggests = TRUE, enhances=TRUE)
```


To create an igraph plot of the dependencies, you can use the function `makeDepGraph()` and plot the results: 

```{r makeDepGraph, warning=FALSE}
dg <- makeDepGraph(tags, includeBasePkgs=FALSE, suggests=TRUE, enhances=TRUE)
set.seed(1)
plot(dg, legendPosEdge = c(-1, 1), legendPosVertex = c(1, 1), vertex.size=20)
```


Note how the dependencies expand to `zoo` (enhanced), `scales` and `ggplot` (suggested) and then recursively from there to get all the Imports and LinkingTo dependencies.



## An example with multiple input packages

A more complicated example:

```{r so-tags, warning=FALSE, fig.width=10, fig.height=10}
tags <- c("ggplot2", "data.table", "plyr", "knitr", "shiny", "xts", "lattice")
pkgDep(tags, suggests = TRUE, enhances=FALSE)

dg <- makeDepGraph(tags, includeBasePkgs=FALSE, suggests=TRUE, enhances=TRUE)
plot(dg, legendPosEdge = c(-1, -1), legendPosVertex = c(1, -1), vertex.size=10, cex=1)
```

